---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  dpi = 300,
  out.width="45%", 
  fig.width=4, 
  fig.height=4
  )
```

# ditherer

This package makes an attempt at implementing full colour ordered (Bayer matrix) dithering in R. The engine behind the image handling is the `magick` package.

## Installation
```{r eval = F}
remotes::install_github('cj-holmes/ditherer)
```

Add package to search path
```{r warning=FALSE, message=FALSE}
library(ditherer)

# ggplot2 for convenience in readme
library(ggplot2)
```

## Typical workflow
Path to original image
```{r}
img <- 'data-raw/lenna.png'
```

Create a target palette for the original image. Here I do that using the `colorfindr` package.
```{r out.width="100%", fig.width=8, fig.height = 1, message=FALSE, warning=FALSE}
# Create a 16 colour target palette from the image
set.seed(1)
tp <-
  colorfindr::get_colors(img) %>% 
  colorfindr::make_palette(n = 16, show = FALSE)

# View the target palette
data.frame(x = tp) %>%
  ggplot(aes(x="", fill = x))+
  geom_bar()+
  coord_flip()+
  scale_fill_identity()+
  theme_void()
```

Recreate the original image using only the target palette
```{r fig.show="hold"}
# Original
dither(img, original = TRUE) + labs(caption="Original")

# Dithered (target palette)
dither(img, target_palette = tp) + labs(caption = "16 colour target palette")
```

## Default target palette
By default, if a target palette is not supplied, `ditherer` uses a uniform palette made of 216 colours.

View the default palette
```{r out.width="100%", fig.width=8, fig.height = 1}
data.frame(x = ditherer::c216) %>% 
  ggplot(aes(x="", fill = x))+
  geom_bar()+
  coord_flip()+
  scale_fill_identity()+
  theme_void()
```

Varying the target palette colour spread `r` factor
```{r fig.show="hold", out.width="33%"}
dither(img, r=1/8) + labs(caption = "r = 1/8 (default)")
dither(img, r=1/6) + labs(caption = "r = 1/6")
dither(img, r=1/4) + labs(caption = "r = 1/4")
```

## Greyscale target palette
```{r}
dither(img, target_palette = grey.colors(8))
```

## Other examples
### Splash
```{r fig.show="hold"}
dither('http://sipi.usc.edu/database/preview/misc/4.2.01.png', original = TRUE) +
  labs(caption = "Original")
  
dither('http://sipi.usc.edu/database/preview/misc/4.2.01.png') +
  labs(caption = "Dithering - default parameters and target palette")
```

### Mandrill (a.k.a. Baboon)
```{r fig.show="hold"}
dither('http://sipi.usc.edu/database/preview/misc/4.2.03.png', original = TRUE) +
  labs(caption = "Original")
  
dither('http://sipi.usc.edu/database/preview/misc/4.2.03.png') +
  labs(caption = "Dithering - default target palette")
```
