---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
  )
```

# ditherer

This is a very early work in progress. EXPERIMENTAL!

Now using `magick` as the main engine

## Installation
```{r eval = F}
remotes::install_github('cj-holmes/ditherer)
```

```{r}
library(ditherer)
```

## Test image
View the (resized) original image by setting `original = TRUE`
```{r}
img <- 'data-raw/arnie.jpg'
dither(img, original = TRUE)
```

## Ordered dithering (default)
Default settings are to extract a 16 colour target-palette from the original (resized image). 
```{r}
dither(img, dither = "ordered")
```

The number of colours in the extracted target palette can be set with `n`.
```{r}
dither(img, dither = "ordered", n=4)
```


A greyscale target-palette of length `n` can be generated
```{r}
dither(img, dither = "ordered", target_palette = "greyscale", n=10)
```

A custom palette can be specified and will be used as is
```{r}
dither(img, dither = "ordered", target_palette = c("black", "red3", "grey50", "tan2"))
```

## Error diffusion dithering
Floyd/Steinberg error diffusion dithering (from the `magick` package) can be specified 
```{r}
dither(img, dither = "diffusion")
```
